How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-05 brains-introduction.tex
+keywords +authors +validation +minor changes

\TB{The next section %(Sec.~\ref{sec:related}) 
describes our hypotheses along with the relevant state-of-the-art on this psycholinguistic matter.
%In Sec.~\ref{sec:protocol}, 
In the section that follows it, 
we detail the empirical protocol and the various assumptions that were made in order to deal with the available empirical material.
%Sec.~\ref{sec:results} 
The results section describes the significant psycholinguistic biases observed during \emph{in vivo} quotation reformulation as well as their epidemiological setting, followed by a discussion and general guidelines for further work in the final section.%Sec.~\ref{sec:conclusion}.
}

>>>>

The next section %(Sec.~\ref{sec:related}) 
describes our hypotheses along with the relevant state-of-the-art on this psycholinguistic matter.
%In Sec.~\ref{sec:protocol}, 
Then, we detail the empirical protocol and the various assumptions that were made in order to deal with the available empirical material.
%Sec.~\ref{sec:results} 
We further describe the significant psycholinguistic biases observed during \emph{in vivo} quotation reformulation as well as their epidemiological setting, followed by a discussion and general guidelines for further work in the final section.%Sec.~\ref{sec:conclusion}.

### 2015-03-05 brains-protocol.tex
+keywords +authors +validation +minor changes

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around casual expressions, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
To filter them out, we exclude all quotes having less than 5 words long or lasting more than 80 days %\seb{it is asymmetrical...}
 (as well as quotes not written in English). If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also exclude it.
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up about 2.43m occurrences (out of 8.16m, i.e. 29.8\%).\footnote{The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.}
%We contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion, 
Even if we lose some real event-related utterances which are present in clusters lasting more than 80 days (such as ``the city is tired of me and the organization and I have run our course together''), we check that our approach essentially fulfills its goals by manually coding a random subsample of 100 excluded clusters: a solid 71\% appear to be entirely irrelevant to our analysis (everyday language rather than quotations), and all but one of the remaining clusters were of relevance to the protocol \TB{set out below.}% in Sec.~\ref{sec:model}.

>>>>

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around casual expressions, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
To filter them out, we exclude all quotes having less than 5 words long or lasting more than 80 days %\seb{it is asymmetrical...}
 (as well as quotes not written in English). If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also exclude it.
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up about 2.43m occurrences (out of 8.16m, i.e. 29.8\%).\footnote{The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.}
%We contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion, 
Even if we lose some real event-related utterances which are present in clusters lasting more than 80 days (such as ``the city is tired of me and the organization and I have run our course together''), we check that our approach essentially fulfills its goals by manually coding a random subsample of 100 excluded clusters: a solid 71\% appear to be entirely irrelevant to our analysis (everyday language rather than quotations), and all but one of the remaining clusters were of relevance to the protocol {set out below.}% in Sec.~\ref{sec:model}.

### 2015-03-05 brainscopycut.tex
Add further authornote, keywords, and note fields
Change \ref's to named references or remove them (apastyle does not number sections)
+keywords +authors +validation +minor changes

% Formatting bibliography
\usepackage{natbib}
\setcitestyle{authoryear,round,semicolon}

@@

\title{How do we copy and paste? The semantic drift of quotations in blogspace}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\author{Sébastien Lerique \& Camille Roth}
\affiliation{Centre d'Analyse et de Mathématique Sociales () \& Centre Marc Bloch ()}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large in vivo experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.}

@@

\bibliographystyle{plainnat}
\bibliography{brainscopycut.bib}

>>>>

% Formatting bibliography
%\usepackage{natbib}
\usepackage[natbibapa]{apacite}
%\setcitestyle{authoryear,round,semicolon}

@@

\title{How do we copy and paste? The semantic drift of quotations in blogspace}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE / USR 3130\\Friedrichstr 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE / USR 3130\\Friedrichstr 191, D-10117 Berlin}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large in vivo experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{word production; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; in vivo psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

@@

\bibliographystyle{apacite}
\bibliography{brainscopycut.bib}
